Supplementary Materials

### 2023-06-30 manuscript/supplementary.tex
supp, methods

  \item \textbf{Non-accessible regions}: masks out centromeres (\texttt{acen} entries in
    \texttt{cytoBand.txt}), with 5Mbp padding on either side. The file of
    passing masks is \path{data/annotation/no_centro.bed}.

@@

@@

\subsection{Optimization Diagnostics}
\label{suppsec:optim}

@@

  \caption{ An optimization diagnostic plot showing the 100 top optima. Heatmap
  colors indicate probability mass for the DFE parameters (top four rows).
Estimates of $\pi_0$ and $\mu$ are shown in the bottom two rows. This is the
optimization plot for YRI Feature Priority model.}

\end{figure}
\clearpage

>>>>

  \item \textbf{Non-accessible regions}: masks out centromeres (\texttt{acen} entries in
    \texttt{cytoBand.txt}), with 5 Mbp padding on either side. The file of
    passing masks is \path{data/annotation/no_centro.bed}.

@@

\subsection{Out-Sample Error Estimation and $R_\text{LOO}^2$}

We fit each of our B' model fits 22 times, excluding a whole chromosome each
time to calculate out-sample prediction error. Each fit used 10,000 random
starting positions as the main fits. The out-sample prediction error for all
bins in chromosome $C$ left out is,

\begin{align}
    SSE(C) = \sum_{b \in C} (\widehat{\pi}_{b,Y\not \in C}  - \pi_b)^2
\end{align}
%

where $\widehat{\pi}_{b,Y\not \in C}$ denotes the predictions for window $b$
fit on data excluding chromosome $C$. The average out-sample error $SSE$ across
chromosomes is then the average of $SSE(C)$ across chromosomes, weighted by the
number of bins per chromosome. We then calculate the out-sample coefficient of
determination $R_\text{LOO}^2$

\begin{align}
    R_\text{LOO}^2 = \frac{SSE}{}
\end{align}

XXX

\subsection{Jackknife Procedures}

\begin{figure}[htbp]
  \label{suppfig:jackknife-iqr}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/supplementary/iqr_jackknife_trim.pdf}

  \caption{The distribution of block jackknife samples for the Feature Priority
  model fit on YRI data. The ranges at the top of the figure indicate the
untrimmed and the 2 IQR-trimmed jackknife intervals. for XXX fix fig }

\end{figure}

We use a block jackknife procedure to calculate the uncertainty of our
estimates. This approach is unfortunately computationally intensive, since a
10Mbp block width requires $\approx 280$ blocks to cover 2.8Gbp of autosomal
sequence and each fit requires thousands of random starts to reliably find
consistent optima. We use a parallelization strategy where a set number of
evenly-spaced positions along the genome that are chosen to approximately cover
all 2.8Gbps of autosomal sequence. Each of these positions is sent out across a
computing cluster, which excludes the 10Mbp block there and fits on the
remaining data. Then, using these jackknife samples we calculated the jackknife
standard error for each of parameters \parencite{Wasserman2004-ip}. In some
cases, our jackknife standard error estimates were very large. Upon inspection
of optimization diagnostic plots (see Supplementary Materials Section
\ref{suppfig:diag-plot}) and histograms of jackknife fits (Supplementary Figure
\ref{suppfig:jackknife-iqr}), these were due to rare aberrant optima. We
removed these using a trimmed-interquartile range, which removes points that
are 2 interquartile ranges below the first quartile or above the third quartile
(1.5 is standard, but we chose to be more conservative to not underestimate
uncertainty).

@@

\subsection{Optimization and Diagnostics}
\label{suppsec:optim}

@@

  \caption{ An optimization diagnostic plot showing the 100 top optima. Heatmap
  colors indicate probability mass for the DFE parameters (top four rows).
Estimates of $\pi_0$ and $\mu$ are shown in the bottom two rows. This is the
optimization plot for YRI Feature Priority model.}
\end{figure}
